Towards Generic Parallel Programming in Computer Science Education with Kokkos

### 2020-10-15 src/5.Example.tex
Final cam-ready version.

    Kokkos::parallel_for("outer", 
      TeamPolicy<>(N,AUTO),
      [=](const member_type &team_handle) {
        const int e = team_handle.league_rank();
        Kokkos::parallel_reduce( 
          TeamThreadRange(team_handle, M),
          [=](const int & i, double & y_tmp) {
            y_tmp += A(e, i) * x(i);
          }, y(e));
    }); 
    Kokkos::fence();
    Kokkos::deep_copy(y_h,y); //copy to host memory space    
  }
  Kokkos::finalize();
}
\end{minted}
\end{small}
\caption{This example application written in Kokkos shows the use of a~\emph{view}-type and a parallel for loop using a ~\emph{TeamPolicy} and a nested parallel reduction. }
\label{fig:KokkosExample}
\end{figure}

>>>>

    Kokkos::parallel_for("outer", 
      TeamPolicy<>(N,AUTO),
      [=](const member_type &team_handle) {
        const int e=team_handle.league_rank();
        Kokkos::parallel_reduce( 
          TeamThreadRange(team_handle, M),
          [=](const int & i, double & y_tmp){
            y_tmp += A(e, i) * x(i);
          }, y(e));
    }); 
    Kokkos::fence();
    //copy to host memory space    
    Kokkos::deep_copy(y_h,y); 
  }
  Kokkos::finalize();
}
\end{minted}
\end{small}
\caption{This example application written in Kokkos shows the use of a~\emph{view}-type and a parallel for loop using a ~\emph{TeamPolicy} and a nested parallel reduction. }
\label{fig:KokkosExample}
\end{figure}
